Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-06-14 Paper/Poster/poster.tex
improved...

\usepackage{epsfig}
\usepackage{multicol}
\usepackage{pstricks,pst-grad}

@@

%%% Section 6
\vspace{0cm}
\begin{center}
  \pbox{0.8\columnwidth}{}{linewidth=2mm,framearc=0.1,linecolor=lightred,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whitepink,gradmidpoint=1.0,framesep=1em}{
    \begin{center}
      \large Pattern Analysis
    \end{center}}
\end{center}

@@

We present two applications of the beat-chroma codebooks
to illustrate how the ``natural'' structure identified via 
unsupervised clustering can provide useful 
features for subsequent supervised tasks.

\vspace{1cm}

%%% CONFUSION MATRIX
\begin{minipage}[c][9cm][c]{0.1\textwidth}
  \begin{center}
    \includegraphics[width=15cm,angle=0]{conf_mat_per_artist.ps}
  \end{center}
\end{minipage}
\begin{minipage}[c][9cm][c]{0.21\textwidth}
  \begin{center}
    fmkefeifiwefi comment on confusion matrix\\
    cjsbdqwb\\
    cecewe
  \end{center}
\end{minipage}

@@

\end{multicols}
\end{poster}
\end{document}

>>>>

\usepackage{epsfig}
\usepackage{multicol}
\usepackage{pstricks,pst-grad}
\usepackage{url}
\usepackage{wrapfig}

@@

%%% Section 4
\vspace{0cm}
\begin{center}
  \pbox{0.8\columnwidth}{}{linewidth=2mm,framearc=0.1,linecolor=lightred,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whitepink,gradmidpoint=1.0,framesep=1em}{
    \begin{center}
      \large Pattern Analysis
    \end{center}}
\end{center}

@@

\vspace{4.0cm}

\begin{minipage}[c][9cm][c]{\columnwidth}

We present two applications of the beat-chroma codebooks
to illustrate how the ``natural'' structure identified via 
unsupervised clustering can provide useful 
features for subsequent supervised tasks.
\vspace{1cm}

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{conf_mat_per_artist.ps}
  \end{center}
  \vspace{-20pt}
\end{wrapfigure}

\textbf{Artist recognition task}.
We use the {\it artist20} data set: $1402$ songs from $20$ artists, 
mostly rock and pop of different subgenres.  
Previously published results using GMMs on MFCC features achieve an 
accuracy of $59\%$, whereas using only chroma as a representation yields an
accuracy of $33\%$  \cite{Ellis2007}.

We get an accuracy of $\mathbf{23.4\%}$, random baseline 
is around $5\%$. 
The confusion matrix is shown here, note 
that certain artists are recognized at an accuracy far above the average.

\end{minipage}

\vspace{2cm}

\begin{minipage}[c][9cm][c]{\columnwidth}
  %\begin{center}
\textbf{Bar alignment task}.
Since the clustering described is based
on the segmentation of the signal in to bars, 
the codewords should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.\\
  %\end{center}
\end{minipage}
\begin{minipage}[c][9cm][c]{0.21\textwidth}
  \begin{center}
      \begin{tabular}{cc}
        Offset & \% of times chosen \\ \hline \hline
        0 & $\mathbf{62.6}$\\
        1 & $16.5$\\
        2 & $9.4$\\
        3 & $11.5$
      \end{tabular}
      %\mytablecaption{\small{
      %    Bar alignment experiment:
      %    offsets relative to ground-truth 4-beat bar boundaries 
      %    that gave minimum distortion encodings from the bar-aligned codebook.
      %}}
      \label{tab:offset}
  \end{center}
\end{minipage}

@@

\end{multicols}

% FOOTNOTE
%\vspace{10cm}
\begin{minipage}{\textwidth}
\begin{flushright}
Poster presented at ISMIR 2010 (Utrecht) for the paper:
Clustering Beat-Chroma Patterns in a Large Music Database by
T. Bertin-Mahieux, R. J. Weiss and D. P. W. Ellis. Contact:
\url{tb2332@columbia.edu}, code: \url{http://www.columbia.edu/~tb2332/}.
\end{flushright}
\end{minipage}

\end{poster}
\end{document}
